Thermodynamic Structure of the Solar Corona: Tomographic Reconstructions and MHD Modeling

### 2020-01-07 lloveras_2020.tex
otros cambios imag

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth,clip=]{figs/histocr2208_cgenergia.eps}
\caption{\albert{Sugiero fuertemente que el histograpma de Type 0 tenga xr=[-1,+3] como el resto, creo que quedará claro por qué cuando lean el análisis que hice de esta Figura en el texto.} {Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
\label{energia_demt}
\end{center}
\end{figure}

>>>>

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccdownenergia.eps}
\includegraphics[width=0.495\textwidth]{figs/histocr2082_ccenergia.eps}
\includegraphics[width=0.495\textwidth]{figs/histocr2208_ccenergia.eps}
\includegraphics[width=0.495\textwidth]{figs/histocr2082_cgenergia.eps}
\includegraphics[width=0.495\textwidth]{figs/histocr2208_cgenergia.eps}
\caption{\albert{Sugiero fuertemente que el histograpma de Type 0 tenga xr=[-1,+3] como el resto, creo que quedará claro por qué cuando lean el análisis que hice de esta Figura en el texto.} {Statistical results of the loop-integrated energy flux quantities $\phi_r,\phi_c,$ and $\phi_h$ in colors blue, red and green, respectively for CR-2082 (left) and CR-2208 (right). From top to bottom, panels show the results for loops of type 0, I and II, which are loops for which both legs meet the criteria from Section \ref{trace}.} \notebyalbert{(by Albert) En el XYOUTS podés poner la letra griega $\phi$ usando los comandos ``!4" y ``!3",  y para que te salga r,c,h como subíndice pero no tan pequeño usá: ``!Dp!N", dónde p=r,c,h.}}
\label{energia_demt}
\end{center}
\end{figure}
